### 2014-03-11 src/conclusion.Rnw
udpate

% For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
% For mutant clustering
%TODO Report time for each, as cost.

Our analysis suggests that random sampling of mutants can help reduce the computational requirements to an extremely large extant while still staying within acceptable accuracy limits.
An interesting finding is that statement deletion did produce as good accuracy in predicting final mutation score as random sampling techniques that offered comparable mutation reduction.

>>>>

Our analysis suggests that simple random sampling, that is, at the project level works best when compared to more sophesticated schemes of sampling. Further, we also note that random sampling performs better in predicting final mutation score when compared against operator selection.

This suggests that the best way to reduce the computational requirements while trying to build a representative set is to randomly sample on the whole set of mutants directly.

### 2014-03-11 src/discussion.Rnw
udpate

\begin{figure}[t]
\includegraphics[totalheight=5cm]{fig/opstrat1.eps}
\caption{Example Mutants}
\label{fig:egmutants}
\end{figure}

@@

>>>>

\begin{figure}[t]
\includegraphics[totalheight=4.5cm]{fig/opstrat1.eps}
\caption{Mutant distribution in a sample project along operators and program elements}
\label{fig:egmutants}
\end{figure}

@@

There may infact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
It is a representation of the distribution of mutants along two orthogonal axes --- the
mutation operators, and program elements such as classes. For the purposes of this
explanation, assume that each classes contain about five lines, and each mutant
produced per line by each of the mutation operators are marked by a small solid circle.
The two solid vertical lines in blue and red represents two classes, one with a relatively
small number of mutants and other with large number of mutants. Further, let use use
$N_{red}$ as the number of mutants in red class, and $N_{blue}$ as the number of mutants
in blue classs, and $N_{blue} > N_{red}$ as shown in figure, and let $N$ be the total
number of mutants, and $C$ the number of classes.

To consider a concrete example, consider two classes with 4 and 2 mutants respectively.
Then -- \textbf{solve} --

What this is saying in effect is that irrespective of the sophestication of sampling used,
the simplest sampling technique --- that of project based sampling --- is the best form of
sampling, for a representative set.

This also applies immediately to operator selection as it is another kind of sampling on
a smaller set. Hence it is no surprise that for larger samples, random sampling is able
to trump operator selection on predicting the final result.

### 2014-03-11 src/related.Rnw
udpate

>>>>

% RAHUL ( I want to emphasise two points here, First is, Budd in 1980 showed
% that 10\% selection lead to less than 1\% accuracy loss, which is confirmed
% by Wong. Further, Wong says that operator selection with 2 operators are
% virtually indistinguishable from x\% selection with 5\%.
% Also, I want to note that their sampling was on top of the operator and not
% directly on project. Finally we should also note that MUA was done on 5 small
% programs.

% Operator Selection also assumes that fault detection ability of some operators
% are higher than others, and hence some operators should have higher weight
% than others. ~\cite{wong1997comparison}

A number of studies in the past have looked at the relative merits of operator
selection and random sampling criteria, starting with Wong and Mathur in
1995~\cite{wong1995reducing}.  They observed that x\% selection up to 10\%
and constrained mutation had similar accuracy, and that constrained mutation
provided similar reduction (80\%) compared to sampling. It is to be noted
that the x\% selection was applied on top of each operator, and not directly
on the whole set of mutants. They used 5 small programs in C and Fortran.

% RAHUL )
